---
title: "12_deu_qualia"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(tidyverse)
library(scales)
library(groupdata2)

ntr_paths = list.files("deu/data/ntr_out", pattern = "*.csv", full.names = T)
shuff_ntr_paths = list.files("deu/data/ntr_shuffled/", pattern = "*.csv", full.names = T)
```

```{r}
deu_full = read_csv("deu/data/02_deu_s.csv")

norm41 = read_csv(ntr_paths[str_detect(ntr_paths, "41")]) %>%
  rename(rowname = doc_id)

shuff41 = read_csv(shuff_ntr_paths[str_detect(shuff_ntr_paths, "41")]) %>%
  rename(rowname = doc_id)

D_41 = left_join(norm41, deu_full, by = "rowname")
D_41S = left_join(shuff41, deu_full, by = "rowname")
```

```{r}
deu_part = read_csv("deu/data/02_deu_raw.csv")

D_41 = left_join(norm41, deu_part, by = "rowname")
D_41S = left_join(shuff41, deu_part, by = "rowname")
```

# party
Party tags are a bit of a mess
But seems like there are some periods of extreme novelty and transience.
Big lump of standard speeches - not following the identity line: 
medium novelty, low transience
```{r}
D_41 %>%
ggplot(aes(z_novelty, z_transience)) +
  geom_bin2d(bins = 100) +
  scale_fill_viridis_c(trans = "log", breaks = c(1,10,100,1000,10000),
                       labels = trans_format("log10", 
                                             math_format(expr = 10^.x, format = force))) +
  facet_wrap(~party) +
  coord_fixed()
```

# position
this is a mess, there are too many positions
```{r}
D_41 %>%
ggplot(aes(z_novelty, z_transience)) +
  geom_bin2d(bins = 100) +
  scale_fill_viridis_c(trans = "log", breaks = c(1,10,100,1000,10000),
                       labels = trans_format("log10", 
                                             math_format(expr = 10^.x, format = force))) +
  facet_wrap(~position) +
  coord_fixed()
```

# period
Pattern is mostly the same across periods
```{r}
D_41 %>%
ggplot(aes(z_novelty, z_transience)) +
  geom_bin2d(bins = 100) +
  scale_fill_viridis_c(trans = "log", breaks = c(1,10,100,1000,10000),
                       labels = trans_format("log10", 
                                             math_format(expr = 10^.x, format = force))) +
  facet_wrap(~period) +
  coord_fixed()
```

# resonance ~ time
the same 
```{r}
D_41 %>%
  ggplot(aes(date, z_resonance)) +
  geom_bin2d(bins = 100) +
  scale_fill_viridis_c(trans = "log", breaks = c(1,10,100,1000,10000),
                       labels = trans_format("log10", 
                                             math_format(expr = 10^.x, format = force)))
```

# resonance ~ time by PARTY
very interesting!
```{r}
D_41 %>%
  ggplot(aes(date, z_resonance, color = parliamentary_group)) +
  geom_smooth()

D_41 %>%
  ggplot(aes(x = lubridate::year(D_41$date), z_resonance, fill = parliamentary_group)) +
  geom_bar(stat = "summary")

table(D_41$parliamentary_group)
party_oi = c("BÜNDNIS 90/DIE GRÜNEN", "SPD")

D_41S %>%
  filter(parliamentary_group %in% party_oi) %>%
  ggplot(aes(x = lubridate::year(date), 
             y = z_resonance, 
             fill = parliamentary_group)) +
  geom_smooth()

D_41S %>%
  ggplot(aes(date, z_resonance, color = parliamentary_group)) +
  geom_smooth()
```

# length of debates by time of day
```{r}
by_day <- group(deu_part, n = 'auto', 
                method = 'l_starts',
                starts_col = 'date', 
                col_name = 'rowname.day') %>%
  mutate(text_nchar = nchar(text_c))

by_day %>%
  ggplot(aes(x = rowname.day, y = text_nchar, group = date)) +
  geom_density(stat = "summary")

by_day %>%
  ggplot(aes(x = rowname.day, y = text_nchar, group = date)) +
  geom_bin2d(bins = 100) +
  scale_fill_viridis_c(trans = "log", breaks = c(1,10,100,1000),
                         labels = trans_format("log10", 
                          math_format(expr = 10^.x, format = force)))

sp_by_day = by_day %>%
  filter(!is.na(date)) %>%
  filter(role != "presidency") %>%
  group_by(date) %>%
  summarise(n = n())
```

# german novelty gate: same speeches?
```{r}
lumpn = D_41 %>%
  filter(z_transience >= 2 & z_novelty >= 2)

lumps = D_41S %>%
  filter(z_transience >= 2 & z_novelty >= 2)

lumpdiff = anti_join(lumpn, lumps, by = "rowname")
```

```{r}
D_41 %>%
  ggplot(aes(z_novelty, z_transience)) +
  geom_bin2d(bins = 100) +
  scale_fill_viridis_c(trans = "log", breaks = c(1,10,100,1000,10000),
                       labels = trans_format("log10", 
                                             math_format(expr = 10^.x, format = force))) +
  coord_fixed()
```

